### 2018-06-26 Thesis/Parts/Discussion/Discussion.tex
Updated ev/mv

Figure~\ref{figure:journalPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. The journals in the center of the plot belong mainly to mixed groups, which is caused by the separation of the medicine field into two groups, with as center journals \textit{Orvosi hetilap} and \textit{Journal of Clinical and Diagnostic Research}.\\
The interactive version shows that the clusterings, as seen on both figure~\ref{figure:journalPlotNormal} \&~\ref{figure:journalPlotGroups} are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates. This problem is already visible in figure~\ref{figure:journalPlotGroups} where, as discussed earlier, the k-means algorithm divided one field into multiple groups. We found that our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The mayor difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human made) partitioning data. They have therefore a more reliable grouping metric.

>>>>

Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the journals in the, what we will refer to as "subject spectrum". We do this because the journal embeddings capture journal-relatedness, which leads to the clustering of related articles, which share, in varying degree, the common subject. In this figure, we can see that the publisher Wiley is more active in the right part of the spectrum than the left. We can further see that Nature is far to the center, as we would expect a generic journal to be, but it is on the biology/medicine side of the center (indicated by the position of Cell and Pharmaceutical Research).\\
Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journals, grouped with k-means on the original 300-dimensional embedding vector. In the plot we can see that the original embedding-clustering, as provided by the k-means algorithm, is relatively well preserved, most groups stay clustered together. 
The interactive version shows that the clusterings, as seen on all four figures, are subject based. Journals concerning the same subjects are correctly clustered together, and the journals in between topic clusters are also positioned at logical positions. It furthermore shows that the k-means groupings create an insight in research fields, although it is limited by the amount of groups the k-means algorithm creates. Our findings on the 2-dimensional representation of embeddings are similar to those of \citet{dai2015document}, who plotted 4.4 million Wikipedia articles. The major difference between our plot and their plot is that they focus on just a view subjects in an entire plot, and have access to (human made) partitioning data. They have therefore a more reliable grouping metric.

### 2018-06-26 Thesis/Parts/Research_results/Research_results.tex
Updated ev/mv

\clearpage
\subheader{F1-Score}
Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_avg_f1}
\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
\end{figure}
\begin{figure}[htb]
\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
\end{figure}
\clearpage
\subheader{Memory usage}
Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.\\
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
\hline
tfidf 5k 5K & $9.82$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
\hline
tfidf 5K 10K & $11.47$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
\hline
\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
\hline
embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
\hline
5k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
\hline
10k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
\hline
\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
\hline
1k 6k embedding & $3.06$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
\hline
\end{tabular}
\end{center}
\caption{Memory usage and performance for each set}\label{table:memoryUsage}
\end{table}
\subheader{Journal relatedness plot}
Figure~\ref{figure:journalPlotNormal} is the two dimensional plot of the journal embeddings. The journals are color-marked by publisher. Red is Wiley, lime is Elsevier and blue is Springer Nature. The grey points are other or not-specified.
Figure~\ref{figure:journalPlotGroups} shows the journals, grouped by a k-means algorithm, creating 8 groups. The bottom right shows the names of the journals closest to the center of the group. The k-means algorithm ran on the 300-dimensional set, while the plot shows the 2-dimensional set.
\begin{landscape}
\begin{figure}
\includegraphics[height=6.5in]{Plots/journal_plot_normal}
\caption{Journal plot grouped by publisher}\label{figure:journalPlotNormal}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\includegraphics[height=6.5in]{Plots/journal_plot_grouped}
\caption{Journal plot grouped k-means grouped}\label{figure:journalPlotGroups}
\end{figure}
\end{landscape}
\end{document}

>>>>

\clearpage
\subheader{F1-Score}
Figures~\ref{figure:f1Title} \&~\ref{figure:f1Abstract} show the precision, recall and f1 scores. These scores are calculated on journal level, and are averaged per set. Figure~\ref{figure:f1Title} shows the F1 score for the title and figure~\ref{figure:f1Abstract} shows the scores for the abstract. These scores indicate the performance of the sets on absolute hits/top-1.
\begin{figure}[hbt]
\includegraphics[width=6.5in]{Plots/Title_avg_f1}
\caption{Precision, recall and F1 scores based on title}\label{figure:f1Title}
\end{figure}
\begin{figure}[htb]
\includegraphics[width=6.5in]{Plots/Abstract_avg_f1}
\caption{Precision, recall and F1 scores based on abstract}\label{figure:f1Abstract}
\end{figure}
\clearpage
\subheader{Memory usage}
Table~\ref{table:memoryUsage} shows the total memory usage of each set for the \textit{Validation set}, indicating their storage costs in gigabytes\footnote{1024 based}.\\
\begin{table}[hbt]
\begin{center}
\begin{tabular}{|l|l|l|l|l|}
\hline
Set & Size in GB & Absolute hit percentage & Median title rank & Median abstract rank\\
&&\begin{tabular}{p{0.5in}|p{0.5in}}Title & Abstract\end{tabular}&&\\
\hline
tfidf 5k 5K & $9.82$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.42\% & 10.18\%\end{tabular} & 50 & 27\\
\hline
tfidf 5K 10K & $11.47$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.49\% & 11.08\%\end{tabular} & 38 & 15\\
\hline
\textbf{tfidf 10K 10K} &\textbf{11.61}& \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{6.79\%} & \textbf{11.32\%}\end{tabular} & \textbf{35} & \textbf{14}\\
\hline
embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.92\% & 9.24\%\end{tabular} & 27 & 23\\
\hline
5k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}6.34\% & 8.36\%\end{tabular} & 42 & 27\\
\hline
10k embedding & $3.13$ & \begin{tabular}{p{0.5in}|p{0.5in}}7.03\% & 8.76\%\end{tabular} & 34 & 25\\
\hline
\textbf{tfidf embedding} & \textbf{3.13} & \begin{tabular}{p{0.5in}|p{0.5in}}\textbf{7.89\%} & \textbf{9.33\%}\end{tabular} & \textbf{27} & \textbf{22}\\
\hline
1k 6k embedding & $3.06$ & \begin{tabular}{p{0.5in}|p{0.5in}}5.16\% & 7.86\%\end{tabular} & 64 &31 \\
\hline
\end{tabular}
\end{center}
\caption{Memory usage and performance for each set}\label{table:memoryUsage}
\end{table}
\subheader{Journal relatedness plot}
We created two seperate journal plot, figures~\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped} show the title based embeddings, and figures~\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped} show the abstract based embeddings.
Figures~\ref{figure:titlePlotNormal} \&~\ref{figure:abstractPlotNormal} show the two dimensional plots of the journal embeddings. The journals are color-marked by publisher. Red is Wiley, lime is Elsevier and blue is Springer Nature. The grey points are other or not-specified publishers.
Figures~\ref{figure:titlePlotGrouped} \&~\ref{figure:abstractPlotGrouped} show the journal embeddings grouped by a k-means algorithm, creating 8 groups. The bottom right shows the names of the journals closest to the center of the group. While most names state the topic of the research field, some do not. These are \textit{RSC Advances}: chemical sciences, and \textit{Symmetry}:  research on symmetry phenomena wherever they occur in mathematical or scientific studies. The k-means algorithm ran on the 300-dimensional vectors, while the plot shows the 2-dimensional vectors. In the title-based figures (\ref{figure:titlePlotNormal} \&~\ref{figure:titlePlotGrouped}) the journals \textit{PNAS} and \textit{Cell} overlap each others labels on the bottom right side of the graph. In the abstract-based figures (\ref{figure:abstractPlotNormal} \&~\ref{figure:abstractPlotGrouped}) the journals \textit{PNAS} and \textit{Nature} overlap each others label on the bottom right side of the graph.
The digital versions of these plots can be found at:~\url{https://goo.gl/nCGMcu} (title-based) and~\url{https://goo.gl/LwYP6k}. The usage of this digital version is advised, since this interactive plot enables zooming and adjusting plot settings, which can give a broader insight into the results than the presented figures. Although the presented figures give sufficient for the purpose of this thesis.
\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_normal}
\end{center}
\caption{Journal plot of title embeddings, grouped by publisher}\label{figure:titlePlotNormal}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_normal}
\end{center}
\caption{Journal plot of abstract embeddings, grouped by publisher}\label{figure:abstractPlotNormal}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Title_grouped}
\end{center}
\caption{Journal plot of title embeddings, k-means grouped}\label{figure:titlePlotGrouped}
\end{figure}
\end{landscape}

\begin{landscape}
\begin{figure}
\begin{center}
\includegraphics[height=6.5in]{Plots/Journal_Plots/Abstract_grouped}
\end{center}
\caption{Journal plot of abstract embeddings, k-means grouped}\label{figure:abstractPlotGrouped}
\end{figure}
\end{landscape}
\end{document}
